Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-12 results.tex
language about mase spread

\svdone behaves very differently than the other seven systems in this
study.  Though its weighted permutation entropy is very high ($0.957
\pm 0.016$), two of the three prediction methods do quite well on this
signal, yielding $MASE$ scores of $0.827 \pm 0.076$ (LMA) and $0.714
\pm 0.075$ (ARIMA).  This pushes the corresponding clusters of points
in the bottom two images in Figure~\ref{fig:wpe_vs_mase_all} well
above the trend followed by the other seven signals.  The $MASE$
scores of the predictions that were produced by the \naive ~method for
this system, however, are highly inconsistent.  The majority of the
blue diamond-shaped points on the top plot in
Figure~\ref{fig:wpe_vs_mase_all} are clustered near a $MASE$ score of
0.6.  In five of the 15 \svdone trials, however, there were step
changes in the signal.  The \naive ~method has a very difficult time
with signals like this, particularly if there are multiple step
changes.  This raised the $MASE$ scores of these trials, pushing the
corresponding points to the right, and in turn raising both the mean
and variance of this set of trials.

>>>>

\svdone behaves very differently than the other seven systems in this
study.  Though its weighted permutation entropy is very high ($0.957
\pm 0.016$), two of the three prediction methods do quite well on this
signal, yielding $MASE$ scores of $0.827 \pm 0.076$ (LMA) and $0.714
\pm 0.075$ (ARIMA).  This pushes the corresponding clusters of points
in the bottom two images in Figure~\ref{fig:wpe_vs_mase_all} well
above the trend followed by the other seven signals.  The $MASE$
scores of the predictions that were produced by the \naive ~method for
this system, however, are highly inconsistent.  The majority of the
blue diamond-shaped points on the top plot in
Figure~\ref{fig:wpe_vs_mase_all} are clustered near a $MASE$ score of
0.6.  In five of the 15 \svdone trials, however, there were step
changes in the signal.  The \naive ~method has a very difficult time
with signals like this, particularly if there are multiple step
changes.  This raised the $MASE$ scores of these trials, pushing the
corresponding points to the right\footnote{This includes the cluster
  of three points near $MASE \approx 2.5$, as well as two points that
  are beyond the domain of the graph, at $MASE$ 11.2 and 14.8.}, and
in turn raising both the mean and variance of this set of trials.
